---
title: "Analysis Project Planning & Stakeholder Updates"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis Projects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ghtrackr)
```

The open science movement has spurred many resources on how to structure large analytical projects in a filesystem for ease of use, collaboration, and reproducibility. These principles apply equally well to research, industry, or personal projects, and often involve the use of GitHub.

A parallel trend noted in different resources in the need for analysts to communicate plans for their large analytical projects. This is an obvious theme in a range of cases, such as Lucy D'Agostino McGowan's blog post on writing a [disertation](https://livefreeordichotomize.com/2018/09/14/one-year-to-dissertate/) and Jen Thompson's blogpost and talk [The Data Person as Project Manager](https://jenthompson.me/2018/10/31/data-person-as-pm/). The nature of analytical works forces analysts to coordinate diverse priorities, seek alignment on their priorities and plan of attack, and provide communication and visibility to stakeholders of various seniority and technical engagement.

Since version control via git and sharing on GitHub are often recommended practices for structuring reproducible analysis projects, using GitHub for the project management component as well reduces the mental overhead of switching between tools. In particular, project planning through GitHub enables natural communication to various consumers of your analysis, whether committee members (as Lucy describes), subject matter experts (as Jen describes), or business leaders.

In particular, Lucy emphasizes the importance of sending out an agenda before meetings and sharing minutes afterward, specifically recapping recently completed work and next steps. Such meetings are another good use for plans to make sure everyone is aligned with an analysts approach.

## Planning Your Project

Writing out your plan of attack in YAML lets you focus on key details and allows everything to remain easily editable while you refine your approach.

Recall the example plan discussed in the vignette on custom plans:

```{r comment='', echo = FALSE}
plan_path <- system.file("extdata", "plan.yml", package = "ghtrackr", mustWork = TRUE)
cat(readLines(plan_path), sep = '\n')
```

As described in the custom plans vignette, this could be added to a GitHub repo as issues and milestones with the `post_plan()` function.

## Including in Meeting Reports

Meeting minutes or agendas can be added to agendas and minutes, such as Lucy's templates provide, with the `report_` functions. 

```{r}
plan_path <- system.file("extdata", "plan.yml", package = "ghtrackr", mustWork = TRUE)
my_plan <- read_plan(plan_path)
report_plan(my_plan)
```

Similarly, as items are accomplished, the complementary `report_progress()` function provides information on in-progress parts of your plan, pulled back down from GitHub.

```{r eval = FALSE}
issues <- 
  get_issues(analysis_repo, state = 'all', since = '2018-12-01') %>% 
  parse_issues() %>%
  filter(issues, milestone_created_at >='2018-12-25' & milestone_created_at <= '2018-12-31') %>%
  arrange(milestone_number)
```

```{r echo = FALSE}
issues <- 
  readRDS(system.file("extdata", "anproj-issues.rds", package = "ghtrackr", mustWork = TRUE))
```

```{r}
report_progress(issues)
```

