---
title: "Use Case: Project Planning & Stakeholder Updates (Posting & reporting custom plans)"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis Projects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ghtrackr)
```


Communicating analytical results is a core part of the data science process. A related but less appreciated task is communcating analysis plans and progress to various stakeholders throughout a project. This need is a recurring theme across disciplines. Lucy D'Agostino McGowan discusses how to lead effective check-ins with dissertation committees in her blog post [One Year to Dissertate](https://livefreeordichotomize.com/2018/09/14/one-year-to-dissertate/) and Jen Thompson describes the central role that "data people" play in project managing cross-functional clinical research teams in her blog post (and related talk) [The Data Person as Project Manager](https://jenthompson.me/2018/10/31/data-person-as-pm/). The same need is also readily apparent in corporate settings where it can be crucial for analysts to articulate how they are spending their time and set expectations on when they can deliver results.

Project management work can sometimes boost productivity and bring benefits, but communcating to stakeholders has significant overhead and can risk stealing time from core job responsibilities. For those "data people" that use R and GitHub, conducting project planning and reporting with the same toolkit can reduce complexity and the inefficiencies of switching between contexts and tools. 

Both Lucy and Jen's recommendations emphasize the importance of facilitating meetings and documentating agreed upon plans and deliverables. `ghtrackr`'s concepts of "plans" provide an interface for these project management tasks. Plans can be created in YAML and delivered to various customers in their preferred format. For the analyst, they can be automatically posted to a GitHub repo as a set of issues and milestones for easy tracking and linking to commits and pull requests. For sharing with senior stakeholders who are not on GitHub, both plans and progress updates can be formatted into aesthetic RMarkdown reports, similar to the examples Lucy's blog shows for meeting agendas and minutes. 

## Planning Your Project in YAML

Writing out your plan of attack in YAML lets you focus on key details and allows everything to remain easily editable while you refine your approach. Lightweight, plain-text YAML can even be tracked by git to record any changes over time.

Recall the example plan discussed in the vignette on custom plans:

```{r comment='', echo = FALSE}
plan_path <- system.file("extdata", "plan.yml", package = "ghtrackr", mustWork = TRUE)
cat(readLines(plan_path), sep = '\n')
```

## Convert YAML to GitHub Milestones and Issues

As described in the custom plans vignette, this could be added to a GitHub repo as issues and milestones with the `post_plan()` function, like this:

```{r eval = FALSE}
plan <- read_plan("plan.yml")
my_repo <- create_repo_ref("emilyriederer", "my_repo_name")
post_plan(plan, my_repo)
```

This can help you keep yourself organized or align priorities with technical collaborators.

## Reporting Project Plans and Progress

To communicate with those not on GitHub, `report_` functions convert plans to HTML which can be inserted into RMarkdown-based meeting agendas, minutes, presentations, or other team communications. 

```{r}
plan_path <- system.file("extdata", "plan.yml", package = "ghtrackr", mustWork = TRUE)
my_plan <- read_plan(plan_path)
report_plan(my_plan)
```

Similarly, as tasks are completed and their related issues are closed on GitHub, that infromation can be pulled back down from GitHub. The complementary `report_progress()` function reformats GitHub issues for a consistent report of an in-progress plan, 

```{r eval = FALSE}
issues <- 
  get_issues(analysis_repo, state = 'all', since = '2018-12-01') %>% 
  parse_issues() %>%
  filter(issues, milestone_created_at >='2018-12-25' & milestone_created_at <= '2018-12-31') %>%
  arrange(milestone_number)
```

```{r echo = FALSE}
issues <- 
  readRDS(system.file("extdata", "anproj-issues.rds", package = "ghtrackr", mustWork = TRUE))
```

```{r}
report_progress(issues)
```

For some audiences, posted plan data could also be show visually with functions such as `viz_gantt()`, which could plot either time-to-completion data or a Gantt plot based on anticipated milestone due dates.

