---
title: "Basic Usage"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette illustrates codeflows of `tidytracker`'s core functionality.

```{r}
library(tidytracker)
```


## Creating a Repo Reference

The first step to interacting with a GitHub repository is creating a repository reference. Repository references are "first class citizens" in `tidytracker` and contain all authorization credentials. These references are passed as the first argument in all `get_` functions.

```{r}
dplyr <- create_repo_ref('tidyverse', 'dplyr')
```

## Getting Issues

`get_` functions retrieve information from the GitHub API. The first argument is the repository reference and additional named query parameters can be passed subsequently. For example, here, we request issues of the first `milestone` with either an open or closed `state`. (Note that, in keeping with the GitHub API, only open issues are returned when `state` is not specified.)

```{r}
dplyr_issues_list <- get_issues(dplyr, milestone = 1, state = 'all')
dplyr_issues <- parse_issues(dplyr_issues_list)
head(dplyr_issues)
```

## Visualizing Issues

There are many different ways to visualize issues. 

For reporting on time-to-completion, `viz_gantt_closed()` creates one horizontal bar per issue and colors issues by length of time open.

```{r}
viz_gantt_closed(dplyr_issues)
```

`viz_taskboard()` creates an Agile-like taskboard of issues open, in progress, and completed.

```{r}
dplyr_issues$closed_at[1] <- NA
dplyr_issues$closed_at[3] <- NA
dplyr_issues$state[c(1,3)] <- "open"
dplyr_issues$labels_name[[3]] <- c("in-progress", dplyr_issues$labels_name[[3]])
viz_taskboard_v2(dplyr_issues, 40)
```

`viz_waterfall_issues()` creates a waterfall plot showing, for a fixed time-period, the initial count of open issues, newly reported issues, closed issues, and final open count. 

```{r}
viz_waterfall_issues(dplyr_issues, '2014-01-01', '2015-01-01')
```



