---
title: "Basic Usage"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette illustrates codeflows of `tidytracker`'s core functionality.

```{r}
library(tidytracker)
```


## Creating a Repo Reference

The first step to interacting with a GitHub repository is creating a repository reference.

```{r}
dplyr <- create_repo_ref('tidyverse', 'dplyr')
```

## Getting Issues

```{r}
dplyr_issues_list <- get_issues(dplyr, milestone = 1, state = 'all')
dplyr_issues <- parse_issues(dplyr_issues_list)
head(dplyr_issues)
```

## Visualizing Issues

There are many different ways to visualize issues. 

For reporting on time-to-completion, `viz_gantt_closed()` creates one horizontal bar per issue and colors issues by length of time open.

```{r}
viz_gantt_closed(dplyr_issues)
```

`viz_taskboard()` creates an Agile-like taskboard of issues open, in progress, and completed.

```{r}
dplyr_issues$closed_at[1] <- NA
dplyr_issues$closed_at[3] <- NA
dplyr_issues$state[c(1,3)] <- "open"
dplyr_issues$labels_name[[3]] <- c("in-progress", dplyr_issues$labels_name[[3]])
viz_taskboard_v2(dplyr_issues, 40)
```

`viz_waterfall_issues()` creates a waterfall plot showing, for a fixed time-period, the initial count of open issues, newly reported issues, closed issues, and final open count. 

```{r}
viz_waterfall_issues(dplyr_issues, '2014-01-01', '2015-01-01')
```



