---
title: "Design Notes"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Design Notes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette details some key design choices in this package with the hope that stating these explicitly will improve package navigability.

## API Function Parameters

In general, parameters required by the GitHub API are required by the corresponding functions in this package. Any additionaly parameters not required by the GitHub API can be passed in through the `...`s. The `browse_docs()` function can be used to find out more about these optional parameters.

## Get-Parse Codeflow

All `get_` functions make a call to the GitHub API and return the result as an R list. The corresponding `parse_` function converts each list into a dataframe for easier wrangling and analysis. In most all cases, users will likely call `parse_` immediately after `get_` and never work with the output of `get_` directly. For example:

```{r eval = FALSE}
my_repo <- create_repo_ref('username', 'my_repo')
issues <- get_issues(my_repo, state = 'all') %>% parse_issues()
issue_events <- get_issue_events(my_repo, number = 7) %>% parse_issue_events()
milestones <- get_milestones(my_repo) %>% parse_milestones()
```

However, the `get_` and `parse_` functions are provided separately to empower users. Some use cases where users may prefer to *not* use the provided `parse_` functions include if they:

- wish to understand the type of output returned by the API
- prefer working with lists than dataframes
- want to access information returned by the API that is not included in the `parse`d output
- need a stop-gap solution should the GitHub API ever change until the `parse_` functions are updated accordingly

## Parse Output Variable Names

As much as possible, the dataframe returned by `parse_` functions maintains the same field names as used by the GitHub API. However, there are a few key exceptions:

- When the field name is ambiguous, additional information may be appended. 
    + For example, after getting an issue, the "comments" field contains the count of comments. Since the name might otherwise suggested that the text of the comments is being returned, the `parsed_` field is instead called "n_comments"
- When the field is nested, underscores are used to provide the hierarchy. 
    + For example, after getting an issue, the "user" field contains multiple subfields about the issue author. Most critical is that user's login, so the field in the resulting dataframe is called "user_login". 
    + This can provide some confusion since other non-hierarchical fields naturally contain underscores, such as the "created_at" date.
