---
title: "Design Notes"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Design Notes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette details some key design choices in this package with the hope that stating these explicitly will improve package navigability.

## Repo as First Class Citizen

Repositories are treated as "first class" citizens. The first step to accessing or sending information is to create a repository reference using the `create_repo_ref()` function. The resulting object is the first element passed into all `get_` and `post_` functions.

For users that work with databases in R with the `DBI` package, this codeflow is analogous to querying from a database. In this case, users first create a database connection object with `dbConnect()` which is passed into subsequent functions such as `dbGetQuery`.

This decision was made under the assumption that working with a single repository would be the most common use case for individual users. Sometimes, users might instead wish for a view further up in the hierarchy, e.g. an organization object versus a repository object. Hopefully, it should be possible to achieve the same results as this would provide by mapping over a set of repositories.

## Function Naming

Functions generally conform to the popular `<verb>_<details>` convention, which is popular across many R packages. For functions interaction with the GitHub API, the `<verb>` component is the HTTP method invoked (e.g. GET, POST, DELETE). 

To users unfamiliar with APIs, verbs like "post" might seem less intuitive than a synonym like "create" or "submit". However, this convention describes the function's action most precisely and ideally also serves to raise awareness of HTTP methods.

## Function Parameters

Functions that interact with GitHub's API demure to the naming conventions of that API. This ideally empowers users for future, direct work with the API or allows for easier maintenance.

More specifically, parameters required by the GitHub API are required by the corresponding functions in this package. Any additionaly parameters not required by the GitHub API can be passed in through the `...`s. The `browse_docs()` function can be used to find out more about these optional parameters.

## Get-Parse Codeflow

All `get_` functions make a call to the GitHub API and return the result as an R list. The corresponding `parse_` function converts each list into a dataframe for easier wrangling and analysis. In most all cases, users will likely call `parse_` immediately after `get_` and never work with the output of `get_` directly. For example:

```{r eval = FALSE}
my_repo <- create_repo_ref('username', 'my_repo')
issues <- get_issues(my_repo, state = 'all') %>% parse_issues()
issue_events <- get_issue_events(my_repo, number = 7) %>% parse_issue_events()
milestones <- get_milestones(my_repo) %>% parse_milestones()
```

However, the `get_` and `parse_` functions are provided separately to empower users. Some use cases where users may prefer to *not* use the provided `parse_` functions include if they:

- wish to understand the type of output returned by the API
- prefer working with lists than dataframes
- want to access information returned by the API that is not included in the `parse`d output
- need a stop-gap solution should the GitHub API ever change until the `parse_` functions are updated accordingly

## Parse Output Variable Names

In keeping with the [Function Parameters], the dataframe returned by `parse_` functions attempt to maintain the same field names as used by the GitHub API. However, there are a few key exceptions:

- When the field name is ambiguous, additional information may be appended. 
    + For example, after getting an issue, the "comments" field contains the count of comments. Since the name might otherwise suggested that the text of the comments is being returned, the `parsed_` field is instead called "n_comments"
- When the field is nested, underscores are used to provide the hierarchy. 
    + For example, after getting an issue, the "user" field contains multiple subfields about the issue author. Most critical is that user's login, so the field in the resulting dataframe is called "user_login". 
    + This can provide some confusion since other non-hierarchical fields naturally contain underscores, such as the "created_at" date.
