---
title: "Timestamping with Events Data"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Timestamping with Events Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ghtrackr)
```

```{r echo = FALSE}
# mock issues data
issues <-
data.frame(
  title = paste("Issue", 1:3),
  body = rep("Hello", 3),
  state = rep("closed", 3),
  created_at = as.Date(c('2018-03-30', '2018-04-02', '2018-04-17')),
  closed_at = as.Date(c('2018-04-30', '2018-04-15', '2018-05-02')),
  user_login = rep('emilyriederer', 3),
  number = 1:3,
  stringsAsFactors = FALSE
)

# mock events data
issue_events <-
  data.frame(
    number = 1:3,
    id = 123:125,
    actor_login = rep('emilyriederer', 3),
    event = rep('labeled', 3),
    created_at = as.Date(c('2018-04-15', '2018-04-02', '2018-04-20')),
    label_name = rep('in-progress', 3),
    milestone_title = NA,
    assignee_login = NA,
    assigner_login = NA,
    stringsAsFactors = FALSE
  )
```


Events data, as returned by `get_issue_events()`, provides a much more granular view of the innerworkins of your GItHub repository. As opposed to the snapshot view returned by `get_issues()`, `get_issue_events()` provides specific times that key changes were made to each issue, such as the addition and deletion of labels and milestones. This is useful if the `created_at` date for your issues don't have intrinsic meaning with regard to when you started working on an issue. 

For example, let's suppose we pull some issues from our repo and visualize their time-to-completion with `viz_gantt_closed()`.

```{r eval = FALSE}
my_repo <- create_repo_ref('emilyriederer', 'my_repo')
issues <- get_issues(experigit, state = 'closed', milestone = 1) %>% parse_issues()
```

```{r}
viz_gantt_closed(issues)
```

Issue 1 stands out as having taken a very long time. However, it's possible it was created a long time before anyone started actively working on it. Instead, we might want to consider the start time to be, for example, when an issue was tagged with the "in-progress label".

We can get events for a specific issue with the following code.Due to the potentially massive size of this data, the function returns events for a single issue at a time and, thus, has a required `number` parameter to specify the issue for which events should be returned. As such, to events for multiple issues, we need to use `purrr::map()`.

Since events can also include adding assignees or milestones, we filter our dataset to `'labeled'` events where the `label_name` is "in-progress".

```{r eval = FALSE}
issue_events <- 
  purrr::map(1:3, ~get_issue_events(experigit, number = .)) %>% 
  purrr::map_df(parse_issue_events) %>%
  dplyr::filter(event == 'labeled' & label_name == 'in-progress')
```

The fields of the resulting dataframe are shown below. 

```{r}
head(issue_events)
```

Next, we can join our datasets together.

```{r}
issue_with_events <- dplyr::inner_join(issues, issue_events, by = "number", suffix = c("", "_event"))
```

Finally, we can use this new dataset to remark our plot by specifying the new `created_at_event` variable as the appropriate issue start date, via the optional `start` parameter.

```{r}
viz_gantt_closed(issue_with_events, start = created_at_event)
```


