---
title: "Timestamping with Events Data"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Timestamping with Events Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(projmgr)
```

```{r echo = FALSE}
# mock issues data
issues <-
data.frame(
  title = paste("Issue", 1:3),
  body = rep("Hello", 3),
  state = rep("closed", 3),
  created_at = as.Date(c('2018-03-30', '2018-04-02', '2018-04-17')),
  closed_at = as.Date(c('2018-04-30', '2018-04-15', '2018-05-02')),
  user_login = rep('emilyriederer', 3),
  number = 1:3,
  stringsAsFactors = FALSE
)

# mock events data
issue_events <-
  data.frame(
    number = 1:3,
    id = 123:125,
    actor_login = rep('emilyriederer', 3),
    event = rep('labeled', 3),
    created_at = as.Date(c('2018-04-15', '2018-04-02', '2018-04-20')),
    label_name = rep('in-progress', 3),
    milestone_title = NA,
    assignee_login = NA,
    assigner_login = NA,
    stringsAsFactors = FALSE
  )
```


Events data, as returned by `get_issue_events()`, provides a granular view of issues in your GitHub repository. As opposed to the issue-level data returned by `get_issues()`, `get_issue_events()` provides timestamped event-level data for each issue, such as the addition and deletion of labels and milestones. See the [Issue Events GitHub API documentation](https://developer.github.com/v3/issues/events/) for a more comprehensive list.

This detailed information has many potential uses. One use in reporting and visualization is if if the `created_at` date for your issues does not have an intrinsic meaning and does not represent when work on an issue was started. 

For example, let's suppose we pull some issues from our repo and visualize their time-to-completion with `viz_gantt()`.

```{r eval = FALSE}
my_repo <- create_repo_ref('emilyriederer', 'my_repo')
issues <- get_issues(experigit, state = 'closed', milestone = 1) %>% parse_issues()
```

```{r}
viz_gantt(issues)
```

Issue 1 stands out as having taken a very long time to complete. However, it's possible it was created long before anyone started actively working on it. Instead, we might want to consider the start time to be, for example, when an issue was tagged with the "in-progress label".

We can get events for a specific issue with the following code. Due to the potentially massive size of this data, the function returns events for a single issue at a time and, thus, has a required `number` parameter to specify the issue for which events should be returned. As such, to events for multiple issues, we need to use `purrr::map()`.

Since events can also include adding assignees or milestones, we filter our dataset to `'labeled'` events where the `label_name` is "in-progress". 

```{r eval = FALSE}
issue_events <- 
  purrr::map(1:3, ~get_issue_events(experigit, number = .)) %>% 
  purrr::map_df(parse_issue_events) %>%
  dplyr::filter(event == 'labeled' & label_name == 'in-progress')
```

The fields of the resulting dataframe are shown below. Note that in this dataset, the `created_at` field refers to when the *event* was created (i.e. when the issue was labelled in this case) and not when the *issue* was created.

```{r}
head(issue_events)
```

Next, we can join our datasets together. THe `suffix` parameter allows us to append `_event` to all the field names from the events data to distinguished between the issue and event `created_at` fields.

```{r}
issue_with_events <- dplyr::inner_join(issues, issue_events, by = "number", suffix = c("", "_event"))
```

Finally, we can use this new dataset to remake our plot by specifying the new `created_at_event` variable as the appropriate issue start date, via the optional `start` parameter.

```{r}
viz_gantt(issue_with_events, start = created_at_event)
```


