---
title: "Wrangling Label and Assignee List Columns"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Wrangling Label and Assignee List Columns}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(projmgr)
```

Most of the information provided by the GitHub API is well-suited for a tabular data structure. Entities like issues and milestones can easily be represented as a row of a dataset, and characteristics about them (e.g. date created, open / closed status) each fit one column. 

The main exception to this rule is assignees and labels as these potentially have a "one-to-many" relationship with issues. (That is, one issue can have multiple assignees or multiple labels.) One way this could have been represented is to create separate key tables for issues-assignees and issues-milestones. However, this seemed like a bulky solution that would result in many unneccesary joins and API calls.

Instead, `parse_issues()` uses [list columns](https://jennybc.github.io/purrr-tutorial/ls13_list-columns.html) to represent assignees and labels. Essentially, the `labels_name` and `assignees_name` columns do not contain character *values* but instead, each row contains its own *list of values*. This may seem unintuitive at first, but list columns are a neat way to rectangularize nested data structures. 

However, wrangling list columns is slightly different than wrangling values due to the extra level of containment. To help effectively work with these list columns, `projmgr` offers three helper functions: `listcol_extract`, `listcol_filter`, and `listcol_pivot`. These are particularly well-suited to help in cases where labels are used to encode issue metadata in some sort of key-value pair. For example, one might use a format like `"priority:high"` to denote importance or `"blue-team"` to denote responsibility.

To see these in action, we will take a snapshot of issues from the RForwards repo.

```{r eval = FALSE}
forwards <- create_repo_ref("forwards", "tasks")
issues <- get_issues(forwards) %>% parse_issues()
```

```{r echo = FALSE}
issues <- readRDS(system.file("extdata", "forwards_issues.rds", package = "projmgr", mustWork = TRUE))
```

As we can see, the `labels_name` column contains lists of entries. 

```{r message = FALSE, warning = FALSE}
library(dplyr)
select(issues, labels_name, number, title) %>% head()
```

One common use of labels in this repo is to denote the team responsible for completing a task, denoted by the tag `"{name}-team"`.

```{r}
unique(unlist(issues$labels_name))
```


## Filter List Column

The `listcol_filter()` lets us filter our data only to the isues relevant to a certain list column entry. For example, the data currently contains 26 issues.

```{r}
nrow(issues)
```

If we are only interested in issues that have been designated for a certain task force, we can filter to those ending with "-team". 

```{r}
listcol_filter(issues, "labels_name", matches = "-team$", is_regex = TRUE) %>% nrow()
```

Even more specifically, if we are members of the teaching team and want to find issues we are responsible for, we can search for an exact match.

```{r}
listcol_filter(issues, "labels_name", matches = "teaching-team") %>% nrow()
```


## Extract List Column

The `listcol_extract()` function creates a new column in the data by checking each element of the list column for a certain structure. For example, we can create a `team` column in our dataset by extracting the labels ending in `"-team"`.

```{r}
select(issues, labels_name, number) %>%
  listcol_extract("labels_name", regex = "-team$") %>%
  head()
```

By default, the function names the new column a "cleaned-up" form of the regex used for matching, but this can be overridden with the `new_col_name` argument. 

```{r}
select(issues, labels_name, number) %>%
  listcol_extract("labels_name", regex = "-team$", new_col_name = "team_name") %>%
  head()
```

By default, the function also drops the regex from the values. This is controlled by the `keep_regex` argument.

```{r}
select(issues, labels_name, number) %>%
  listcol_extract("labels_name", regex = "-team$", keep_regex = TRUE) %>%
  head()
```

Unlike the above example, sometimes multiple items will match a given regex. In this case, a list-column is added to the dataset containing any matches. 

For example, the third entry of the `assignees_login` field contains 4 logins. Two contain the letter "d".

```{r}
issues$assignees_login[[3]]
```

Now, `listcol_extract()` returns a list-column. For the third entry, this list column has length 2.

```{r}
select(issues, assignees_login, number) %>%
  listcol_extract("assignees_login", regex = "d", keep_regex = TRUE) %>%
  head()
```


## Pivot List Column

Finally, the `listcol_pivot()` helped function identifies all labels matching a regex, extract all the "values" from the key-value pair, and pivots these into boolean columns. For example, the following code makes a widened dataframe with a separate column for each team. `TRUE` denotes the fact that that team is responsible for that issue.

```{r}
issues_by_team <-
select(issues, number, labels_name) %>%
  listcol_pivot("labels_name", 
                regex = "-team$",
                transform_fx = function(x) sub("-team", "", x), 
                delete_orig = TRUE) 

head(issues_by_team)
```

This has many convenient use-cases, including being able to quickly see the number falling into each category.

```{r}
issues_by_team %>% select(-number) %>% summarize_all(sum)
```

## A tidyr alternative

Besides these helper columns, another convenient way to work with these list columns is by using `tidyr::unnest()` to create key tables mapping issue numbers (`number`) to the label names (`labels_name`) or assignees (`assignees_login`).

```{r message = FALSE, warning = FALSE}
library(tidyr)
```

For example, below we select only the issue number and the labels name columns.

```{r}
issues_labels <-
  issues %>%
  select(number, labels_name) %>%
  unnest()

head(issues_labels)
```

The same can be done to map between issue numbers and assignees.

```{r}
issues_assignees <-
  issues %>%
  select(number, assignees_login) %>%
  unnest()

head(issues_assignees)
```

Logic could then be done on these key tables to identify relevant issue numbers and joined / filtered back on to the complete issues dataframe.
