---
title: "Reporting with RMarkdown"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reporting with RMarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(projmgr)
```

Communication is a critical part of project planning. For this, `projmgr` provides a family of `report` functions. These functions translate certain R objects like lists or dataframes into HTML code which will render nicely when knitted to HTML in an RMarkdown document.

## Plans & To-Do Lists

Recall that plans and to-do lists can be written in YAML. For example:

```{r comment='', echo = FALSE}
plan_path <- system.file("extdata", "plan.yml", package = "projmgr", mustWork = TRUE)
cat(readLines(plan_path), sep = '\n')
```

The `report_plan()` function converts plans into formatted HTML for inclusion in RMarkdown documents for more aesthetic reporting.

```{r}
plan <- read_plan(plan_path)
report_plan(plan)
```

The `report_todo()` function works similarly.

## Issues & Milestones

Similarly, any issue-milestone data pulled back down from GitHub can be reported in a similar format with `report_progress()`.

```{r echo = FALSE}
issues <- 
  readRDS(system.file("extdata", "anproj-issues.rds", package = "projmgr", mustWork = TRUE))
```

```{r}
report_progress(issues)
```

## Discussions

Additionally, full issues discussions can be pulled from GitHub and reformatted to HTML for long-term documentation with the `report_discussion()` function.

```{r eval = FALSE}
issues <- get_issues(experigit, number = 163) %>% parse_issues()
comments <- get_issue_comments(experigit, number = 163) %>% parse_issue_comments()
```

```{r echo = FALSE}
issues <- readRDS(system.file("extdata", "disc-issues.rds", package = "projmgr", mustWork = TRUE))
comments <- readRDS(system.file("extdata", "disc-comments.rds", package = "projmgr", mustWork = TRUE))
```

```{r}
report_discussion(comments, issues)
```

