---
title: "Reporting with RMarkdown"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reporting with RMarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(projmgr)
```

Communication is a critical part of project planning. For this, `projmgr` provides a family of `report` functions. These functions translate certain R objects like lists or dataframes into HTML code which will render nicely when knitted to HTML in an RMarkdown document.

## Plans & To-Do Lists

Recall that plans and to-do lists can be written in YAML. For example:

```{r comment='', echo = FALSE}
plan_path <- system.file("extdata", "plan.yml", package = "projmgr", mustWork = TRUE)
cat(readLines(plan_path), sep = '\n')
```

The `report_plan()` function converts plans into formatted HTML for inclusion in RMarkdown documents for more aesthetic reporting.

```{r}
plan <- read_plan(plan_path)
report_plan(plan)
```

The `report_todo()` function works similarly.

## Issues & Milestones

Similarly, any issue-milestone data pulled back down from GitHub can be reported in a similar format with `report_progress()`.

```{r echo = FALSE}
issues <- 
  readRDS(system.file("extdata", "anproj-issues.rds", package = "projmgr", mustWork = TRUE))
```

```{r}
report_progress(issues)
```

## Taskboards

```{r echo = FALSE}
pkg_issues <- readRDS(system.file("extdata", "viz-issues-data.rds", package = "projmgr", mustWork = TRUE))
pkg_issues$url <- ""
```

Using HTML and CSS grid, the `report_taskboard()` function also offers aesethetic and interactive views of your work.

```{r}
report_taskboard(pkg_issues, in_progress_when = is_assigned_to("emilyriederer"))
```

Users specify what logic to use for identifying "in progress" items by passing a function factory to the `in_progress_when` parameter. The above example uses the `is_labeled_with()` option. Other options include:

```{r}
ls('package:projmgr')[grep("^is_*", ls('package:projmgr'))]
```

See `?taskboard_helpers` for more details.

Optional parameters of this function are `include_link` (whether to link back to the relevant GitHub issue), `hover` (for slightly enlarging a task on hover), and `colors` (to provide a character vector of colors to override the defaults.) 

As a second example, suppose we instead classify issues as in progress once they have been put in a milestone.

```{r}
report_taskboard(pkg_issues, 
                 in_progress_when = is_in_a_milestone(),
                 include_link = FALSE,
                 hover = TRUE,
                 colors = c('#ff0000', '#00ff00', '#0000ff'))
```

## Discussions

Additionally, full issues discussions can be pulled from GitHub and reformatted to HTML for long-term documentation with the `report_discussion()` function.

```{r eval = FALSE}
issues <- get_issues(experigit, number = 163) %>% parse_issues()
comments <- get_issue_comments(experigit, number = 163) %>% parse_issue_comments()
```

```{r echo = FALSE}
issues <- readRDS(system.file("extdata", "disc-issues.rds", package = "projmgr", mustWork = TRUE))
comments <- readRDS(system.file("extdata", "disc-comments.rds", package = "projmgr", mustWork = TRUE))
```

```{r}
report_discussion(comments, issues)
```

