---
title: "Integrating reprex and clipr"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Integrating reprex and clipr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

[`reprex`](https://www.tidyverse.org/help/) is a great package to help package users and developers communicate by allowing for the sharing of reproducible examples. 

`tidytracker` can play along with `reprex` by facilitating posting reprexes to repos as well as pulling them back down to evaluate them.

## Posting reprexes

Much like other types of issues, `tidytracker` make it easy to post issues containing reprexes to GitHub.

For example, suppose you have the problematic code on your clipboard, open in a file, or somewhere that `reprex` can find it (refer to the `reprex` package documentation for details). You could post this as the body of an issue with the following code:

```{r eval = FALSE}
reprex::reprex(venue = "gh")
post_issue(tidytracker,
           title = "this is a descriptive title of my issue",
           body = paste( clipr::read_clip(), collapse = "\n") )
```

## Getting and running reprexes

Suppose you see on GitHub that a user posted an issue, say number 82, with a reprex. Admittedly, you could just copy this directly from GitHub like a sane person. However, should you wish to do this with `tidytracker`, you can!

For example:

```{r eval = FALSE}

# get issue in question from repo
experigit <- create_repo_ref('emilyriederer', 'experigit')
issue <- get_issues(experigit, number = 82)

# extract the body containing the reprex (code + output as markdown)
issue[[1]][["body"]] %>% clipr::write_clip()

# strip markdown formatting to revert to initial state
reprex::reprex_invert()

# then paste to console
```

