---
title: "Use Case: Working Offline (Posting custom to-do lists)"
author: "Emily Riederer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Working Offline}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`ghtrackr` allows you to collect issues when working offline and easily post them to a repository later. This provides a productivity boost when you're forced offline by travel or a bad internet connection or prefer to be offline to minimize distractions. 

Issues can be collected either as a dataframe (and posted with code similar to that shown in the KPI Tracking vignette) or as a to-do list. For example, as you encounter new issues, you can keep a running list of them as YAML. (This can be done either by assigning to an R variable or by saving a separate .yml file. Please see the vignette on Custom Plans for more details.)

```{r}
todo_yaml <- "
- title: Add update functions
  body: Issue labels especially could benefit by PATCH or POST/DELETE functionality
  assignees: emilyriederer
- title: Consider adding interactive visualizations
- title: Add function(s) to open GitHub API docs 
  labels: [enhancement, priority:low]
"
```

Then, once you have internet again (which you can check with `check_internet()`), you can simply post all of these items at once.

```{r eval = FALSE}
repo <- create_repo_ref("emilyriederer", "my_gh_repo")
todo <- read_todo(todo_yaml)
post_todo(repo, todo)
```

Of course, even if you have an internet connection, posting issues from R can also help you resist the temptation to go online and get distracted. As you think of new issues, you can simply just post them from the console. For example:

```{r eval = FALSE}
post_issue(
  title = 'Add YAML validators to read_ functions',
  body = 'read_ functions should check for correct plan structure (field names & relationships)',
  labels = 'enhancement'
)
```

